\bibitem{wikisent}
Википедия. Анализ тональности текста. --- \\
\href{http://ru.wikipedia.org/wiki/%D0%90%D0%BD%D0%B0%D0%BB%D0%B8%D0%B7_%D1%82%D0%BE%D0%BD%D0%B0%D0%BB%D1%8C%D0%BD%D0%BE%D1%81%D1%82%D0%B8_%D1%82%D0%B5%D0%BA%D1%81%D1%82%D0%B0}{http://ru.wikipedia.org/wiki/анализ\_тональности\_текста}

\bibitem{dimresearch}
The Impact Of Customer Service On Customer Lifetime Value. --- \url{http://www.zendesk.com/resources/customer-service-and-lifetime-customer-value}

\bibitem{aif}
Любителей покупать в интернете не отвадить обманом. --- \url{http://www.aif.ru/mymoney/article/54692}

\bibitem{medianation}
Как отзывы на Яндекс.Маркет влияют на продажи. --- \url{http://www.medianation.ru/blog/kak-otzyvy-na-yandeks-market-vliyayut-na-prodazhi.php}

\bibitem{twitter_users}
Аудитория Twitter выросла на 60 миллионов человек за год. --- \url{http://lenta.ru/news/2013/03/21/twohundred/}

\bibitem{Pang2008}
Pang B., Lee L. Opinion Mining and Sentiment Analysis // Foundations and 
Trends in Information Retrieval, v.2 n.1-2, January, 2008 - pp.1-135.

\bibitem{Go2009}
Go A., Bhayani R., Huang L. Twitter Sentiment Classification using Distant Supervision // Processing , 2009, pp.1-6 .

\bibitem{Liu2010}
Bing Liu. Sentiment Analysis: A Multi-Faceted Problem // IEEE Intelligent Systems, 2010

\bibitem{wiki_middling}
Викисловарь. Посредственный --- \href{http://ru.wiktionary.org/wiki/%D0%BF%D0%BE%D1%81%D1%80%D0%B5%D0%B4%D1%81%D1%82%D0%B2%D0%B5%D0%BD%D0%BD%D1%8B%D0%B9}{http://ru.wiktionary.org/wiki/посредственный}

\bibitem{Liu2010a}
Bing Liu. Sentiment Analysis and Subjectivity // Handbook of Natural Language Processing, 2010

\bibitem{Wiegand2010}
Wiegand M., Balahur A., Roth B., Klakow D., Montoyo. A. A Survey on the Role of Negation in Sentiment Analysis // Workshop on Negation and Speculation in Natural Language Processing, 2010

\bibitem{Tsur2010}
Oren T., Dmitry D., Ari R. ICWSM – A Great Catchy Name: Semi-Supervised Recognition of Sarcastic Sentences in Online Product Reviews // AAAI Conference on Artificial Intelligence, 2010 

\bibitem{Saif2012}
Saif H., He Y., Alani H. Alleviating Data Sparsity for Twitter Sentiment Analysis // Workshop on Making Sense of Microposts, 2012

\bibitem{streaming}
Twitter Streaming API --- \url{https://dev.twitter.com/docs/streaming-apis}

\bibitem{Lin2012}
Lin J., Kolcz A. Large-Scale Machine Learning at Twitter // ACM SIGMOD International Conference on Management of Data, New York, 2012

\bibitem{sentiment_mapreduce}
Basic sentiment analysis using MapReduce --- \url{http://www.alex-hanna.com/tworkshops/lesson-6-basic-sentiment-analysis/}

\bibitem{Irokez2012}
Обучаем компьютер чувствам (sentiment analysis по-русски) --- \url{http://habrahabr.ru/post/149605/}

\bibitem{rule_romip1}
Kan D. Rule-based approach to sentiment analysis // Sentiment Analysis Track at ROMIP, 2011

\bibitem{rule_romip2}
Паничева П. Сиcтема cентиментного анализа ATEX, оcнованная
на правилах, при обработке текcтов различных тематик // Sentiment Analysis Track at ROMIP, 2012

\bibitem{sentiwordnet}
SentiWordNet --- \url{http://sentiwordnet.isti.cnr.it/}

\bibitem{anew}
Affective Norms for English Words (ANEW) --- \url{http://csea.phhp.ufl.edu/media/anewmessage.html}

\bibitem{Manning2008}
Manning D., Raghavan P., Schütze H. Introduction to Information Retrieval // Cambridge University Press, 2008

\bibitem{wiki_vectorspace}
Википедия. Векторная модель --- \href{http://ru.wikipedia.org/wiki/%D0%92%D0%B5%D0%BA%D1%82%D0%BE%D1%80%D0%BD%D0%B0%D1%8F_%D0%BC%D0%BE%D0%B4%D0%B5%D0%BB%D1%8C}{http://ru.wikipedia.org/wiki/Векторная\_модель}

\bibitem{classifier_performance} 
Оценка классификатора (точность, полнота, F-мера) --- \url{http://bazhenov.me/blog/2012/07/21/classification-performance-evaluation.html}

\bibitem{naive_bayes}
Наивный байесовский классификатор --- \url{http://bazhenov.me/blog/2012/06/11/naive-bayes.html}

\bibitem{Pang2002}
Pang B., Lee L., Vaithyanathan S. Thumbs up? Sentiment Classification using Machine Learning Techniques // ACL-02 conference on Empirical methods in natural language processing, 2002, v. 10, pp. 79-86

\bibitem{Sanders}
Twitter Sentiment Corpus --- \url{http://www.sananalytics.com/lab/twitter-sentiment/}

\bibitem{SemEval2013}
SemEval-2013 --- \url{http://www.cs.york.ac.uk/SemEval2013-2013/task2/}

\bibitem{emoticons}
Wikipedia. List of emoticons --- \url{http://en.wikipedia.org/wiki/List_of_emoticons}

\bibitem{dictionary}
Opinion Lexicon --- \url{http://www.cs.uic.edu/~liub/FBS/sentiment-analysis.html#lexicon}

\bibitem{mutualinformation}
Взаимная информация --- \url{http://bazhenov.me/blog/2012/12/10/feature-selection.html}